Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
Small grammar fix.

The core of our trace optimization technique can be
viewed as partial evaluation: the partial evaluation
performs a form of escape analysis \cite{bruno_blanchet_escape_2003} on the traces and make some
objects that are allocated in the trace \emph{static,} which
means that they do not occur any more in the optimized trace. This technique is
informally described in Section~\ref{sec:statics}; a more formal description is
given in Section~\ref{sec:formal}.

>>>>

The core of our trace optimization technique can be
viewed as partial evaluation: the partial evaluation
performs a form of escape analysis \cite{bruno_blanchet_escape_2003} on the traces and makes some
objects that are allocated in the trace \emph{static,} which
means that they do not occur any more in the optimized trace. This technique is
informally described in Section~\ref{sec:statics}; a more formal description is
given in Section~\ref{sec:formal}.
